06_DESeqALL

### 2019-12-31 analysis/06_DESeq2_ALL.Rmd
new volcano plots

plot_grid(charicons, char2, nrow = 2, rel_heights = c(0.9,1))
```

>>>>

plot_grid(charicons, char2, nrow = 2, rel_heights = c(0.9,1))

timing2 <- plot_grid( 
          n , 
          o + theme(axis.title.y = element_blank(), axis.text.y = element_blank())+
            labs(x = "Log fold change,")   , 
          NULL,
          p + theme(axis.title.y = element_blank(), axis.text.y = element_blank()) +
            labs(x = "pituitary") , 
          q + theme(axis.title.y = element_blank(), axis.text.y = element_blank()) ,
           NULL,
          r + theme(axis.title.y = element_blank(), axis.text.y = element_blank()) , 
          s + theme(axis.title.y = element_blank(), axis.text.y = element_blank()),
            nrow = 1, rel_widths = c(1.4,1, 0.5, 1, 1, 0.5, 1, 1))

plot_grid(timingicons, timing2, nrow = 2, rel_heights = c(0.9,1))
```
